Learning constraints in tabular data

### 2016-05-12 Paper/ECAI/tabular.tex
rewriting paper strucutre

The question that we answer in this paper is: whether it is possible to discover or reconstruct structural constraints (relations, functions) in flat tabular spreadsheet data?
To answer this question we contribute a general-purpose algorithm and system for discovering such constraints. Furthermore, the algorithm accepts declarative specifications of the constraints and predicates of interest (the "bias") and covers both textual and numeric fields. It works in an unsupervised setting, as only the tabular data is provided and no examples need to be specified, and discovers column- and row-wise constraints.
We demonstrate the utility of our approach in an experimental evaluation.
Moreover, we sketch several application scenario's, such as autocompletion and error detection.
\\\\
This paper is organized as follows.
Section \ref{sec:formalization} introduces concepts relevant to our approach. Section \ref{sec:problem_statement} presents our problem statement. Section \ref{sec:approach} describes our approach. Section \ref{sec:evaluation} presents the evaluation of the approach. Section \ref{sec:applications} shows how our system can be used for autocompletion and error detection. Section \ref{sec:related_work} present an overview of the related work. And Section \ref{sec:conclusions} provides conclusions.

>>>>

The question that we answer in this paper is: whether it is possible to discover or reconstruct structural constraints (relations, functions) in flat tabular spreadsheet data?
To answer this question we contribute a general-purpose algorithm and system for discovering such constraints. Furthermore, the algorithm accepts declarative specifications of the constraints and predicates of interest (the "bias") and covers both textual and numeric fields. It works in an unsupervised setting, as only the tabular data is provided and no examples need to be specified, and discovers column- and row-wise constraints.
We demonstrate the utility of our approach in an experimental evaluation.
Moreover, we sketch several application scenario's, such as autocompletion and error detection.
\\\\
This paper is organized as follows.
Section \ref{sec:formalization} introduces concepts relevant to our approach. Section \ref{sec:problem_statement} presents the problem statement. Section \ref{sec:approach} describes the approach. Section \ref{sec:evaluation} presents the evaluation of the approach. Section \ref{sec:applications} shows how our system can be used for applications such as autocompletion and error detection. Section \ref{sec:related_work} present an overview of the related work. And Section \ref{sec:conclusions} provides conclusions.
